---
title: "Context and enrichment/depetion of DMRs with respect to CGI features"
author: "Peter Hickey"
date: "13 November 2016"
output:
  github_document:
    toc: true
    toc_depth: 2
---

```{r, include=FALSE, setup}
knitr::opts_chunk$set(echo = FALSE, comment = "#>", collapse = TRUE, 
                      message = FALSE, results = "hide", warning = FALSE)
load("../objects/assays-and-features.rda")
source("../scripts/functions.R")
```

```{r, message = FALSE, pkgs}
library(GenomicRanges)
library(rtracklayer)
library(readr)
library(ggplot2)
library(dplyr)
library(UpSetR)
```

# CGI context of DMRs and bigDMRs

Using all POS DMRs

## DMRs

```{r, DMRs-CGI-context}
feature_names <- names(cgi_features)
dmrs_pos_hits <- unlist(lapply(feature_names, function(feature_name) {
  setNames(sum(overlapsAny(dmrs_pos, cgi_features[[feature_name]])), feature_name)
}))
dmrs_pos_hits_df <- data.frame(db = "UCSC",
                                      feature = names(dmrs_pos_hits),
                                      hits = unname(dmrs_pos_hits),
                                      perc = 100 * unname(dmrs_pos_hits) / 
                                        length(dmrs_pos),
                                      stringsAsFactors = FALSE)
split(dmrs_pos_hits_df, dmrs_pos_hits_df$db)
x <- makeUpSetRList(dmrs_pos, cgi_features)
upset(fromList(x), order.by = "freq", nsets = length(x))
```

- Vast majority of DMRs in open sea

## DMR-CpGs

Counting CpGs in DMRs rather than number of DMRs

```{r, DMR-CpGs-CGI-context}
feature_names <- names(cgi_features)
dmrs_pos_cpgs_hits <- unlist(lapply(feature_names, function(feature_name) {
  setNames(sum(overlapsAny(dmrs_pos_cpgs, 
                           cgi_features[[feature_name]])), feature_name)
}))
dmrs_pos_cpgs_hits_df <- data.frame(db = "UCSC",
                                           feature = names(dmrs_pos_cpgs_hits),
                                           hits = unname(dmrs_pos_cpgs_hits),
                                           perc = 100 * unname(dmrs_pos_cpgs_hits) / 
                                             length(dmrs_pos_cpgs),
                                           stringsAsFactors = FALSE)
split(dmrs_pos_cpgs_hits_df, dmrs_pos_cpgs_hits_df$db)
x <- makeUpSetRList(dmrs_pos_cpgs, cgi_features)
upset(fromList(x), order.by = "freq", nsets = length(x))
```

- And, unsurprisingly, most DMR-CpGs are in open sea

## bigDMRs

```{r, bigDMRs-CGI-context}
feature_names <- names(cgi_features)
big_dmrs_pos_hits <- unlist(lapply(feature_names, function(feature_name) {
  setNames(sum(overlapsAny(big_dmrs_pos, 
                           cgi_features[[feature_name]])), feature_name)
}))
big_dmrs_pos_hits_df <- data.frame(db = "UCSC",
                                          feature = names(cgi_features),
                                          hits = unname(big_dmrs_pos_hits),
                                          perc = 100 * unname(big_dmrs_pos_hits) / 
                                            length(big_dmrs_pos),
                                          stringsAsFactors = FALSE)
split(big_dmrs_pos_hits_df, big_dmrs_pos_hits_df$db)
x <- makeUpSetRList(big_dmrs_pos, cgi_features)
upset(fromList(x), order.by = "freq", nsets = length(x))
```

- Vast majority of bigDMRs are in open sea

## bigDMR-CpGs

Counting CpGs in bigDMRs rather than number of bigDMRs

```{r, bigDMR-CpGs-CGI-context}
feature_names <- names(cgi_features)
big_dmrs_pos_cpgs_hits <- unlist(lapply(feature_names, function(feature_name) {
  setNames(sum(overlapsAny(big_dmrs_pos_cpgs, 
                           cgi_features[[feature_name]])), feature_name)
}))
big_dmrs_pos_cpgs_hits_df <- 
  data.frame(db = "UCSC",
             feature = names(cgi_features),
             hits = unname(big_dmrs_pos_cpgs_hits),
             perc = 100 * unname(big_dmrs_pos_cpgs_hits) / 
               length(big_dmrs_pos_cpgs),
             stringsAsFactors = FALSE)
split(big_dmrs_pos_cpgs_hits_df, big_dmrs_pos_cpgs_hits_df$db)
x <- makeUpSetRList(big_dmrs_pos_cpgs, cgi_features)
upset(fromList(x), order.by = "freq", nsets = length(x))
```

- And, unsurprisingly, most bigDMR-CpGs are in open sea

# CGI enrichment/depletion of DMR-CpGs and bigDMR-CpGs

Using all POS DMRs

```{r}
or_dmrs_pos_cpgs_cgi <- cbind(
  FT(dmrs_pos_cpgs, non_dmrs_pos_cpgs, cgi_features, "UCSC"),
  data.frame(source = factor("DMR-CpGs", 
                             c("DMRs", "bigDMRs", "DMR-CpGs", "bigDMR-CpGs"))))
or_big_dmrs_pos_cpgs_cgi <- cbind(
  FT(big_dmrs_pos_cpgs, non_big_dmrs_pos_cpgs, cgi_features, "UCSC"),
  data.frame(source = factor("bigDMR-CpGs", 
                             c("DMRs", "bigDMRs", "DMR-CpGs", "bigDMR-CpGs"))))
ggplot(rbind(or_dmrs_pos_cpgs_cgi, or_big_dmrs_pos_cpgs_cgi), 
       aes(x = feature, y = log2(estimate), col = db)) + 
  geom_point() + 
  geom_errorbar(aes(ymin = log2(lower), ymax = log2(upper))) + 
  geom_hline(yintercept = 0) + 
  facet_wrap(~ source, ncol = 2) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) + 
  ggtitle("All genes") + 
  ylab("log2(OR) with 95% CI")
```

### DMR-CpGs

- Enriched in shores, shelves, and CGIs, depleted in open sea

### bigDMR-CpGs

- Enriched in shelves and shores, depleted in CGI and open sea
